Figures

### 2018-06-11 figures/06_k.Rmd
align iws and nws panels

```{r read_chunks, cache=FALSE, echo=FALSE}
knitr::read_chunk("../scripts/03_viz.R")
knitr::read_chunk("../scripts/99_utils.R")
```

```{r source_utils, message=FALSE, results='hide', echo=FALSE, warning=FALSE}

@@

```{r 06_k, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider's equation in low and high connectivity partitions at the (A) LWS and (B) NWS scales. Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=5, fig.height=3.8, warning=FALSE}

>>>>

```{r read_chunks, cache=FALSE, echo=FALSE}
# knitr::read_chunk("../scripts/03_viz.R")
knitr::read_chunk("../scripts/99_utils.R")
```

```{r source_utils, message=FALSE, results='hide', echo=FALSE, warning=FALSE}
# setwd("scripts")
# source("99_utils.R")
```

```{r 06_k, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider's equation in low and high connectivity partitions at the (A) LWS and (B) NWS scales. Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=7, fig.height=3.8, warning=FALSE}

fit_df_iws <- rbind(
  extract_coefs(readRDS("../data/global_vollenweider.rds"), "k"), 
  extract_coefs2(readRDS("../data/lc_vollenweider.rds"), 
                 c("k1_lc", "k2_lc")),
  extract_coefs2(readRDS("../data/md_vollenweider.rds"), 
                 c("k1_md", "k2_md")),
  extract_coefs2(readRDS("../data/iws/cd_vollenweider.rds"),
                 c("k1_cd", "k2_cd")),
  extract_coefs2(readRDS("../data/iws/ll_vollenweider.rds"),
                 c("k1_ll", "k2_ll")),
  extract_coefs2(readRDS("../data/iws/bf_vollenweider.rds"),
                 c("k1_bf", "k2_bf")),
  extract_coefs2(readRDS("../data/iws/sd_vollenweider.rds"),
                 c("k1_sd", "k2_sd")),
  extract_coefs2(readRDS("../data/iws/sr_vollenweider.rds"), 
                 c("k1_sr", "k2_sr")))
  #               extract_coefs2(fit_wc, c("k1_wc", "k2_wc")),

# controls ordering of ridge plot
fit_df_iws$key <- factor(fit_df_iws$key, levels = c("k",
                                                    "k1_sr", "k2_sr",
                                                    "k1_bf", "k2_bf",
                                                    "k1_md", "k2_md",
                                                    "k1_lc", "k2_lc",
                                                    "k1_sd", "k2_sd",
                                                    "k1_cd", "k2_cd",
                                                    "k1_ll", "k2_ll"))

k_viz_iws <- ggplot(
  fit_df_iws, 
  aes(x = coef, y = key, fill = key, color = key)) + 
    geom_density_ridges(size = 0.1, scale = 1) + 
    scale_fill_manual(values = c("grey", 
                            rep(c(viridis::viridis(1, begin = 0.5), 
                                  viridis::viridis(1, begin = 0)), 7))) +
    scale_color_manual(values = c("grey", 
                               rep(c(viridis::viridis(1, begin = 0.5), 
                                     viridis::viridis(1, begin = 0)), 7))) +
    cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
                                     axis.title = element_text(size = 12),
                               plot.title = element_text(size = 12, face = "plain", hjust = 0),
                                     axis.line.x = element_line(size = 1, 
                                     colour = "black"),
                                     axis.line.y = element_line(size = 1, 
                                                       colour = "black"), 
                                     legend.position = "none", 
                                     plot.margin = margin(0.5,0,0,0, "cm")) + 
  xlab("Coefficient Value") + ylab("") + 
  scale_y_discrete(breaks = levels(fit_df_iws$key)[
    c(1, seq(3, length(levels(fit_df_iws$key)), by = 2))], 
                   labels = rev(c("Link length",
                   "Closest lake distance",
                   "Stream density",
                   "Lake connection", 
                   "Max depth",
                   "Baseflow",
                   "Stream order ratio",
                   "Global")))

k_viz_iws

fit_df_nws <- rbind(
  extract_coefs(readRDS("../data/global_vollenweider.rds"), "k"), 
  extract_coefs2(readRDS("../data/lc_vollenweider.rds"), 
                 c("k1_lc", "k2_lc")),
  extract_coefs2(readRDS("../data/nws/cd_vollenweider.rds"), 
                 c("k1_cd", "k2_cd")),
  extract_coefs2(readRDS("../data/nws/ll_vollenweider.rds"), 
                 c("k1_ll", "k2_ll")),
  extract_coefs2(readRDS("../data/nws/la_vollenweider.rds"), 
                 c("k1_la", "k2_la")),
  extract_coefs2(readRDS("../data/md_vollenweider.rds"), 
                 c("k1_md", "k2_md")),
  extract_coefs2(readRDS("../data/nws/bf_vollenweider.rds"), 
                 c("k1_bf", "k2_bf")),
  extract_coefs2(readRDS("../data/nws/sd_vollenweider.rds"), 
                 c("k1_sd", "k2_sd")),
  extract_coefs2(readRDS("../data/nws/sr_vollenweider.rds"), 
                 c("k1_sr", "k2_sr")))

# align iws and nws panel rows
fit_df_nws <- dplyr::filter(fit_df_nws, fit_df_nws$key %in% fit_df_iws$key)

fit_df_nws$key <- factor(fit_df_nws$key, levels = c("k",
                                                    "k1_sr", "k2_sr",
                                                    "k1_bf", "k2_bf",
                                                    "k1_md", "k2_md",
                                                    "k1_lc", "k2_lc",
                                                    "k1_sd", "k2_sd",
                                                    "k1_cd", "k2_cd",
                                                    "k1_ll", "k2_ll"))

k_viz_nws <- ggplot(
  fit_df_nws, 
  aes(x = coef, y = key, fill = key, color = key)) + 
  geom_density_ridges(size = 0.1, rel_min_height = 0.03, scale = 1) + 
  scale_fill_manual(values = c("grey",
                               rep(c(viridis::viridis(1, begin = 0.5),
                                     viridis::viridis(1, begin = 0)), 8))) +
  scale_color_manual(values = c("grey", 
                               rep(c(viridis::viridis(1, begin = 0.5), 
                                     viridis::viridis(1, begin = 0)), 8))) +
  cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
                                   axis.title = element_text(size = 12),
                               plot.title = element_text(size = 12, face = "plain", hjust = 0),
                                   axis.line.x = element_line(size = 1, 
                                                  colour = "black"),
                                   axis.line.y = element_line(size = 1, 
                                                  colour = "black"), 
                                   legend.position = "none", 
                                   plot.margin = margin(0.5,0,0,-0.7, "cm")) + 
  xlab("Coefficient Value") +  ylab("") +
  scale_y_discrete(breaks = levels(fit_df_nws$key)[
    c(1, seq(3, length(levels(fit_df_nws$key)), by = 2))], 
    labels = rev(c("Link length",
                   "Closest lake distance",
                   "Stream density",
                   "Lake connection", 
                   "Max depth",
                   "Baseflow",
                   "Stream order ratio",
                   "Global")))

k_viz_nws

plot_grid(
  k_viz_iws + ggtitle("A. LWS scale") + xlim(0.8, 1.6),
  k_viz_nws + ggtitle("B. NWS scale") + xlim(0.8, 1.6), 
  ncol = 2, align = "v", rel_widths = c(1, 1)) + 
  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"))

@@

### 2018-06-11 manuscript/appendix.Rmd
align iws and nws panels

```{r iws_vs_nws-gis, cache = TRUE}
# lagoslakeid <- 6302
# iws <- pull_iws(lagoslakeid, maxsteps = Inf)
# nws <- pull_nws(lagoslakeid, maxsteps = Inf)
# focal_lake <- 
# upstream_lakes <- 
# saveRDS(iws, "../data/iws_extent.rds")
# saveRDS(nws, "../data/nws_extent.rds")

@@

```{r best_partition_maps, cache=TRUE}
# setwd("manuscript")

@@

                           ggplot() + 
                             geom_sf(data = us_states) +
                             geom_sf(data = nes_sf, 
                                     color = viridis::viridis(1, begin = 0),
                                     size = 0.6) + 
                             geom_sf(data = nes_sub,
                                     color = viridis::viridis(1, begin = 0.5), 
                                     size = 0.6) + 
                             coord_sf(datum = NA) + 
                             ggtitle(break_word(partition_splits[x, "abb"], 12)) + 
                             theme(plot.margin = unit(c(0, -0.1, 0, -0.1), "cm"), 
                               plot.title = element_text(face = "plain", size  = 12))
                         })

>>>>

```{r iws_vs_nws-gis, cache = TRUE, echo=FALSE}
# lagoslakeid <- 6302
# iws <- pull_iws(lagoslakeid, maxsteps = Inf)
# nws <- pull_nws(lagoslakeid, maxsteps = Inf)
# focal_lake <- 
# upstream_lakes <- 
# saveRDS(iws, "../data/iws_extent.rds")
# saveRDS(nws, "../data/nws_extent.rds")

@@

```{r best_partition_maps, cache=TRUE, echo=FALSE}
# setwd("manuscript")

@@

                           ggplot() + 
                             geom_sf(data = us_states) +
                             geom_sf(data = nes_sf, 
                                     color = viridis::viridis(1, begin = 0),
                                     size = 1) + 
                             geom_sf(data = nes_sub,
                                     color = viridis::viridis(1, begin = 0.5), 
                                     size = 1) + 
                             coord_sf(datum = NA) + 
                             ggtitle(break_word(partition_splits[x, "abb"], 12)) + 
                             theme(plot.margin = unit(c(0, -0.1, 0, -0.1), "cm"), 
                               plot.title = element_text(face = "plain", size  = 12))
                         })

### 2018-06-11 manuscript/figures.Rmd
align iws and nws panels

```{r 06_k, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider's equation in low and high connectivity partitions at the (A) LWS and (B) NWS scales. Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=5, fig.height=3.8, warning=FALSE}
knitr::include_graphics("../figures/06_k-1.pdf")
```

>>>>

```{r 06_k, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider's equation in low and high connectivity partitions at the (A) LWS and (B) NWS scales. Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=5, fig.height=3.8, warning=FALSE}
knitr::include_graphics("../figures/06_k-3.pdf")
```
